\documentclass[10pt]{article}

% Fix the list in the SKILLS section
\usepackage{enumitem} % Allows for adding options to lists
\usepackage[margin=1in]{geometry}
\usepackage{setspace} 
\usepackage{multicol}
\usepackage{hyperref}

\newcommand{\mailto}[1]{
  \href{mailto://#1}{\textit{#1}}
}

\newcommand{\linkedin}[1]{
  \href{https://linkedin.com/in/#1}{\textit{linkedin.com/in/#1}}
}

\begin{document}

  % \name{William Setzer}
  % \contact{william@setzer.tech}{334-300-7107} % chktex 8
  \begin{flushright}
    \textbf{William Setzer}

    \mailto{william@setzer.tech}

    \linkedin{william-setzer}
  \end{flushright}

  \bigskip

  Dear Sir or Madame,

  \bigskip

  Customer-focused professional offering experience in computer programming, data collection, data processing, and analysis, with knowledge in Java and Python.


  Bachelor of Computer Science with Honors, \textit{Magna Cum Laude} \hfill May 2018 \\
  University of Alabama at Birmingham \hfill Birmingham, Alabama \\
  GPA\@: 3.81


  \begin{itemize}[nosep]% [topsep=0em, itemsep=-0.5em]
    \item Collected data using Python, Ruby, and PostgreSQL from Reddit and alternative social media sites, e.g. 4chan, 8chan, Minds.
    \item Analyzed collected data with Python and Hadoop to find statistical patterns, producing plots to visualize the data using various plots, e.g. CDFs, CCDFs, joint distributions, and basic scatter and line plots.
    \item Used change point analysis to correlate changes in the patterns of data collected to real-world events.
  \end{itemize}

  \begin{itemize}[nosep]
    \item Instructed lab sections for both Introduction to Computer Science and Computer Architecture, teaching and assisting a wide variety of students as they learned Python in the introductory course and x86 Assembly in the computer architecture course.
    \item Graded homework assignments.
  \end{itemize}

  \begin{itemize}[nosep]
    \item Supervised the programming team, ensuring the quality of code and the delivery of tools for use by the lab's cybercrime analysts.
    \item Established effective use of version control and documentation practices.
    \item Conducted programmer interviews and onboarded new team members.
  \end{itemize}

  \begin{itemize}[nosep]% [topsep=0em, itemsep=-0.2em]

    \item Created efficient web scrapers to scrape forums in \textbf{Python} using packages including \textit{Requests}, \textit{lxml}, \textit{aiohttp}, \textit{AsyncIO}, \textit{multiprocessing}, and \textit{Selenium}.
    \item Transitioned web scraping in the lab from pure Selenium to Requests, AsyncIO, and aiohttp to create faster web scrapers.
    \item Created a web forum database for scrapers in \textbf{PostgreSQL} to replace multiple non-standardized ways of storing forum data.
    % \item Transitioned web scraping database from PostgreSQL to \textbf{MongoDB}, allowing for easier database inserting and queries and easier analysis by the client.
    \item Set up and maintained a \textbf{MongoDB} instance for collecting a variety of non-standard data collected from the web.
          
  \end{itemize}







\end{document}
