\documentclass[10pt]{setzerresume}

    % \usepackage{ebgaramond}

\usepackage{enumitem} % Allows for adding options to lists
\usepackage[margin=0.5in]{geometry}
\usepackage{setspace} 
\usepackage{multicol}
\usepackage{hyperref}

\begin{document}

  \name{William Setzer}
  \contact{\mailto{william@setzer.tech}}{334-300-7107}{\linkedin{william-setzer}} % chktex 8

  \centerline { Professional programmer $|$ Python enthusiast $|$ Problem solver }

  \section{Summary}
  % Customer-focused professional offering experience in computer programming, data collection, data processing, and analysis, with knowledge in Java and Python.
  Customer-focused professional with a passion for data science offering experience in computer programming, data collection, data processing, and analysis, with knowledge in Python, Golang, Java, and relational databases.

  \section{Skills and Languages}

  \begin{itemize}[nosep]
    \item Strong knowledge of Python, Java, Golang, Linux
    \item Good knowledge of PostgreSQL and Snowflake
    \item Familiar with JavaScript, Ruby, and Scala
    \item Beginner proficiency in German
  \end{itemize}

  \section{Education}
  Bachelor of Computer Science with Honors, \textit{Magna Cum Laude} \hfill May 2018 \\
  University of Alabama at Birmingham \hfill Birmingham, Alabama \\
  GPA\@: 3.81


  \section{Work Experience}

  \jobheading{Software Engineer}{August 2021 -- Present}{Shipt}{Birmingham, Alabama} %chktex 8

  \begin{itemize}[nosep]
    \item Utilized Python and later a combination of Python and Golang for efficient ingestion of partners' catalog data
    \item Enhanced our data ingestion framework by implementing parallel and asynchronous processing to handle large partner files and varied partner APIs
    \item Streamlined the onboarding process for new retail partners by creating a data mapping template
    \item Managed program execution through Airflow and GCS Cloud Console
    \item Facilitated data transfer between services using AWS, GCS, and Kafka
    \item Contributed to the overhaul of the ingestion system by leveraging Golang
    \item Collaborated in the design and implementation of new features and APIs
    \item Ensured code reliability through creation and maintenance of robust unit and integration tests
  \end{itemize}

  \jobheading{Junior Software Developer}{May 2020 -- August 2021}{Seneca Resources}{Birmingham, Alabama} %chktex 8

  \begin{itemize}[nosep]
    \item Operated as a junior software developer at Blue Cross and Blue Shield of Alabama.
    \item Contributed to the development and maintenance of the \textit{my}BlueCross website using Java, JavaScript, and HTML.
    \item Designed and implemented REST API endpoints in the Spring framework for Java.
    \item Wrote queries in SQL for IBM Db2 and integrated them into Spring with JDBC. %chktex 13
    \item Modernized the style of web pages according to specification using CSS and SCSS. %chktex 13
    \item Conducted unit tests and documented features using JUnit
    \item Collaborated effectively with team members to achieve project goals
  \end{itemize}


  \jobheading{Cyber Security Engineer}{June 2019 -- May 2020}{Regions Bank}{Birmingham, Alabama} %chktex 8

  \begin{itemize}[nosep]
    \item Redesigned processes to align with modern standards and best practices
    \item Automated SOC processes using the Splunk Phantom platform.
    \item Developed playbooks, automation scripts, and product integrations within Phantom.
    \item Integrated the SOAR platform with a range of products to provide automation actions for workflows.
    \item Migrated content from Demisto to Splunk's Phantom platform
  \end{itemize}


  \jobheading{Research/Teaching Assistant}{August 2017 -- June 2019}{UAB Department of Computer Science}{Birmingham, Alabama} % chktex 8

  \begin{itemize}[nosep]% [topsep=0em, itemsep=-0.5em]
    \item Collected data using Python, Ruby, and PostgreSQL from Reddit and alternative social media sites and forums, e.g. 4chan, 8chan, Minds.
    \item Analyzed collected data with Python and Hadoop to find statistical patterns, producing plots to visualize the data using various plots, e.g. CDFs, CCDFs, joint distributions, and basic scatter and line plots.
    \item Used change point analysis to correlate changes in the patterns of data collected to real-world events.
    \item Instructed lab sections for both Introduction to Computer Science and Computer Architecture, teaching and assisting a wide variety of students as they learned Python in the introductory course and x86 Assembly in the computer architecture course.
    \item Graded homework assignments.
  \end{itemize}


  \jobheading{Programming Team Lead \& Programmer}{April 2017 -- August 2018}{UAB Computer Forensics Research Lab}{Birmingham, Alabama} % chktex 8

  \begin{itemize}[nosep]% [topsep=0em, itemsep=-0.2em]

    \item Supervised the programming team, ensuring the quality of code and the delivery of tools for use by the lab's cybercrime analysts.
    \item Established effective use of version control and documentation practices.
    \item Conducted programmer interviews and onboarded new team members.
    \item Created efficient web scrapers to scrape forums in \textbf{Python} using packages including \textit{Requests}, \textit{lxml}, \textit{aiohttp}, \textit{AsyncIO}, \textit{multiprocessing}, and \textit{Selenium}.
    \item Transitioned web scraping in the lab from synchronously usinig Selenium to Requests, AsyncIO, and aiohttp to create faster web scrapers.
    \item Created a web forum database for scrapers in \textbf{PostgreSQL} to replace multiple non-standardized ways of storing forum data.
    % \item Transitioned web scraping database from PostgreSQL to \textbf{MongoDB}, allowing for easier database inserting and queries and easier analysis by the client.
    \item Set up and maintained a \textbf{MongoDB} instance for collecting a variety of non-standard data collected from the web.
          
  \end{itemize}


  \jobheading{Barista}{May 2016 -- November 2016}{Starbucks}{Birmingham, Alabama} % chktex 8

  \jobheading{Cashier}{January 2016 -- May 2016}{Chick-fil-A}{Birmingham, Alabama} % chktex 8

  \jobheading{Prosthetic Technician}{May 2013 -- June 2013, December 2015 -- January 2016}{Alabama Artificial Limb and Orthotics Service}{Montgomery, Alabama} % chktex 8

  \jobheading{Website Product Entry}{June 2014 -- August 2014}{Beth's Heirloom Sewing}{Wetumpka, Alabama} % chktex 8

  \section{Awards and Leadership}

  \begin{itemize}
    \item \itemanddate{UAB President's List}{Spring 2016, Fall 2016, Fall 2017, Spring 2018}
    \item \itemanddate{UAB Dean's List}{Fall 2015, Spring 2017}
    \item \itemanddate{UAB Presidential Scholarship}{Fall 2014 -- Spring 2018} % chktex 8
    \item \itemanddate{Vermeer Corporation Scholarship}{2014, 2016}
  \end{itemize}

  % \section{Volunteer Experience}


\end{document}
